A Dataset of Operator-client Dialogues Aligned with Database Queries for End-to-end training

### 2016-06-28 paper.tex
od changes and rewrote the worst paragraph

\title{A Dataset of Operator-client Dialogues Aligned with Database Queries}

@@

\maketitle
% \OP{Fill missing values about the dataset collected so far} \\
% \OP{grammar check} \\
\OD{Přemýšlím, jestli ten název neudělat nějak míň popisný a víc vysvětlující (něco o end-to-end dialogue systems)?}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}\label{sec:intro}
\vspace{-0.50em}
We present a new dataset of human-human task-oriented conversations in the restaurant information domain, suitable for supervised training of autonomous systems. 
Currently, the dataset contains only \OP{62} dialogues because we are still collecting more data, but we estimate we will have more than 700 dialogues until the camera ready deadline.\OD{We are currently collecting data for the set using crowdsourcing. We have collected 62 dialogues so far; more than 700 dialogues are planned for the final version of the dataset.\footnote{\OD{We expect to release the set before the camera-ready deadline.}}}

We aim at representing the conversation in a way that makes it easy to train an automated system to replace a human operator. 
In contrast to previously released datasets, our dataset contains easy-to-collect high-quality transcriptions of the client and operator actions during conversations.\OD{tady úplně nevím, k čemu se kontrastuješ}
We introduce a~very little overhead by collecting database calls in addition to the transcription of the conversation.
In fact, we mimic very closely a~real situation in call centers where operators search for answers through a database user interface. 
Just logging the calls to the task database provide us with information of a similar quality as a full manual dialogue state annotation, but not annotated incrementally after each turn.\OD{od “but” nerozumím}
Tracking the database calls in task oriented systems together with conversation transcription should not introduce significant overhead during the data collection, but should presumably boost end-to-end conversational agent as much as annotated dialogue state when training with such data.\OD{but should provide a similar amount of supervision for training an end-to-end conversational agent as using fully annotated dialogue state ??}

Current Spoken Dialogue Systems (SDS) are either handcrafted and use no training data~\cite{duvsek2014alex,raux2005let} but require non-trivial amount of expert work, or they are gradually improved from initial policy through live user interaction~\cite{young2010hidden,gasic2011line}. Recently, SDS have also been trained using supervised learning in an end-to-end manner~\cite{wen2016network,williams2016end}.\footnote{The~work of \cite{williams2016end} also fine-tuned the conversation with reinforcement learning after the supervised learning stage.}
To train a system using reinforcement learning, one only needs to collect enough live user conversation containing explicit feedback.
However, the feedback signal is harder to interpret than supervised annotation: Thousands of live conversations are required to improve a rather simple policy.\cite{gasic2011line}
Supervised learning methods reduced the number of conversations needed for training a reasonable policy down to a few hundreds\cite{wen2016network}, but require explicit annotation for all components used in the dialogue system.
To our knowledge, all current systems require full dialogue state annotation as a minimum~\cite{wen2016network,young2010hidden}.\OD{Tuhle větu asi do footnotu?}
With the dialogue state being a simplification of the dialogue history with no broadly-accepted form, it is very expensive to collect such annotated data because the dialogue state typically differs among domains and its structure is hard to explain to annotators.
In this paper, we focus on collecting a supervised training set with annotation rich enough so that supervised models similar to~\cite{wen2016network} can be trained with a few hundreds of dialogues, yet much easier to collect than previous methods.

We believe that our dataset dataset can be used for first experiments in training end-to-end systems using supervised learning without explicit dialogue state annotation.
The restaurant information domain used in our dataset is well established thanks to dialogue state tracking (DST) challenges~\cite{williams2013dstc1,henderson2014dstc2,henderson2014dstc3}. 
The DST challenges proved that the domain is of a reasonable complexity.
In addition, the challenges showed that the DST task is solvable by architectures which may be extended to end-to-end conversational agents~\cite{platek2016recurrent,vodolan2015hybrid,henderson2014word}.
Note that \ODdel{we collected human-to-human dialogues on Cambridge restaurant domains, but} our data-collection method is \OD{completely} domain independent.

The paper is structured as follows: Section~\ref{sec:repre} motivates the annotation and data formats\OD{?} used in our dataset.
In Section~\ref{sec:collection}, we introduce our collection process using crowdsourcing.
Section~\ref{sec:props} presents the dataset properties, and we list related work in Section~\ref{sec:related}.
We conclude the paper and suggest future work in~Section~\ref{sec:conc}.

@@

\section{Supervised Feedback for Task-oriented Dialogue} \label{sec:repre}
\vspace{-0.50em}
We present a dataset for training a task-oriented conversational agent in a well-defined domain.\OD{In this paper, we assume that we need to train a...}
We assume that the agent has a task database\footnote{In the Cambridge restaurant domain the database is a simple table containing information about restaurants.} at hand and plays the role of the {\it operator}.
The other interlocutor in the conversation is a~human {\it client}.\OD{that seeks information stored in the database}
Clients seek information stored in the database and use the system, which replaced a~human operator, to obtain desired information.\OD{A tuhle větu už pak můžeš vyhodit.}

We focus on data collection for text-to-text task-oriented dialogue systems.
Traditionally, one would train the pipeline of components of task-oriented dialogue systems, i.e., automatic speech recognition (ASR), language understanding (LU) unit, dialogue tracker (DT), dialogue manager (DM), natural language generator (NLG) for text-to-text conversational agents and text-to-speech (TTS) module~\cite{duvsek2014alex}.
However, only the text-to-text pipeline of LU, DT, DM, and NLG is typically trained using just in-domain data~\cite{gasic2011line,jurvcivcek2014factored,duvsek2016sequence}.
The ASR~\cite{platek2014free} and the TTS~\cite{taylor2009text} modules are typically trained using larger datasets.
Our datasets contains data for training an~end-to-end system solving task of LU, DT, DM and NLG pipeline of traditional architecture.\OD{Tenhle odstavec bych ještě trochu překopal.}

% Me to nesedi jako related work - related work je o sbirani dat
% Tohle me prijde zduvodneni, ze takovy (maly, supervised) dataset dava smysl
% Zatim nechavam zde: \OD{následující dva odstavce zní dost jako “related work”... možná bych to tam částečně popřesouval? a tady nechal jen ten statement, že stačí málo trénovacích dat?}
It was shown that a few hundreds of annotated domain specific conversations are needed to train a relatively well performing LU~\cite{jurvcivcek2014factored} as well as Dialogue State Tracking~\cite{young2010hidden} components.\OD{“few” = málo, “a few” = pár, několik}
The work of~\cite{duvsek2016sequence} and~\cite{mairesse2010phrase} showed that only several hundreds of turns with appropriate annotation is needed for training a usable NLG unit in simple domains.
Even the crucial task of action selection can be trained using a POMDP dialogue manager\OD{přepsal bych na “using reinforcement learning”, protože nikde nedefinuješ, co je POMDP} and few thousands conversations despite the fact that rewards are only provided at the end of a dialogue~\cite{gasic2011line}.

@@

We realize that a more fine-grained annotation helps to train the models faster, but simply collecting more data is often more beneficial.\OD{citace? a nevím, jestli tady ta věta je nutná. Možná bych vynechal všechno až do “we believe that annotating...”??}
As a consequence, we regard the works~\cite{wen2016network,bordes2016learning,williams2016end} as an important step forward to reducing the need for rich annotation in dialogue agent training.
We believe that annotating the dialogue state according to an expert-handcrafted ontology is both an~artificial and a~very labor-intensive data collection task. Therefore, our work aims at collecting conversation with lighter and easier to get annotation.
We suggest recording conversation between a human operator and a human clients via a crowdsourcing platform, i.e., collecting cheap high quality training data.
A similar recording setup is known from call centers where the operator is provided with a database interface so that they quickly find relevant information and play the role of a domain expert.
For our dataset, we collect the operator's database calls instead of dialogue state annotation after each turn.\OD{Asi bych tohle dal hned po “eaiser to get annotation”. Pak tu větu “a similar recording setup...” a až na konec “we suggest crowdsourcing”, který bych změnil na “To obtain the dataset, we record conversations between human operators and human clients...”}

@@

\section{Dataset Collection Process} \label{sec:collection}
\vspace{-0.50em}
Our data collection process aims at obtaining natural in-domain conversations.
We decided to collect the dataset within the~well studied Cambridge restaurant domain since previous datasets~\cite{williams2013dstc1,henderson2014dstc2,henderson2014dstc3} in that domain demonstrated that a meaningful and reasonable-length conversations can be held here.\OD{tady už se částečně opakuješ, na jednom místě to zkrať}
Also, it was proven that the domain is on one hand difficult enough that even the state-of-the art systems do not reach human-level performance in the role of the operator~\cite{henderson2014dstc2} and on the other hand, numerous systems~\cite{young2010hidden,gasic2011line,wen2016network} demonstrated their ability to provide information to the clients with a reasonable quality.

We define our domain by choosing the database from the 2nd Dialogue State Tracking Challenge (DSTC2)~\cite{henderson2014dstc2}.
We use the database for steering the dialogue of the two human interlocutors a~{\it client} and an~{\it operator}.\OD{tuhle větu bych vynechal}
We use the CrowdFlower (CF) crowdsourcing platform to collect the conversations.

@@

We use exactly the same database as provided for the DSTC2 challenge~\cite{henderson2014dstc2}.
The database contains information about 107 restaurants in Cambridge, and their properties are stored in several columns.
We include in brackets the number of different values for each column:
\vspace{-0.50em}\OD{Když dáš dvousloupcovou tabulku, tak i ušetříš trochu místa}
\begin{itemize}  % tabulku misto tohohle?
    \item name (107),
    \item price range (4),
    \item area (7),
    \item food (25),
    \item address (101),
    \item phone number (97),
    \item postcode (62).
\end{itemize}
\vspace{-0.50em}

@@

We use this database to generate\OD{prepare} client goals for CF users (see Figure~\ref{fig:client}).
The database is also available through a simple interface to CF users playing the role of the operator (see Figure~\ref{fig:operator}).\OD{nechceš tu odkazovat na ty podsekce spíš než na ty obrázky?}

@@

The CF worker playng the role of the client is asked to request specific information from the operator – a goal.
They may choose not to seek the goal immediately but submit more appropriate response such as greeting instead.
The goals are displayed to the CF worker in the client role gradually turn-by-turn and may contradict each other.
For example, the client may at first want a to find a restaurant serving Chinese food, but later change their mind and seek British food.

Before submitting a reply, the client is instructed to read the dialogue history and mark the goals which were already presented to the operator, as demonstrated in Figure~\ref{fig:client}.\OD{teď nevím, jestli “goal” je celkový cíl, nebo jestli jich má ten worker víc -- to by bylo potřeba jednotně.}
By marking which goals have already been presented to the operator, we force\OD{oblige?} the CF workers to pay attention to the dialogue history before submitting their reply.\OD{do footnotu explicitně vysvětlit, proč to tak je -- proč nemůžou klikat náhodně (že další user vlastně kontroluje toho předchozího tím, že musí zaškrtnout nadmnožinu dříve zaškrtnutých cílů)?}
In Section~\ref{sec:async}, we describe how we combine the workers' replies to form a conversation.\OD{tuhle větu na začátek sekce?}

@@

\vspace{-1.00em}
\subsection{Operator Interface}
\label{sec:operator}
The operator CF worker is asked to politely address the clients needs according to the information stored in the database.
In order to provide the information to clients, the operator uses the simple database interface depicted in~Figure~\ref{fig:operator}:
They filter the restaurants using a full text search over the database.
The content of the database is intentionally hidden if no filter is specified so that a filter has to be used to provide results.
The CF workers are also instructed to explicitly mark the database rows to which they refer in their answer.
Similarly to the client role, the operator does not have to provide all requested information in a single turn.
It is left up to the~worker which information is provided first.

Our full text search interface to the database is implemented in Javascript as a simple substring matching over values in the database.
Multiple constrains can be expressed by two substrings separated by a comma.
We used such a simple interface because it is easy to generate and also reconstruct the candidate results given the query and the database.\OD{co znamená “easy to generate”? hlavně taky “easy to use for untrained CF workers”, to mi přijde důležitější, ne? možná bych ty detaily o tom interfacu hodil rovnou za “using a full text search over the database”}
\ODdel{The CF workers were instructed to mark a candidate row from the results about which they inform in their reply.}\OD{tady se opakuješ}

@@

\vspace{-1.00em}
\subsection{Asynchronous collection without real-time responses}
\label{sec:async}
We design the crowdsourcing jobs so that the CF contributors are able to work independently of each other.
The roles of client and operator take turns as partial conversations are submitted to CF for collecting a single new response.\OD{přijde mi, že “sets of” to spíš zamlží}
As a consequence, a~single conversation is collected from multiple contributors over several job submissions.

@@

In a~single CF task submission, we let the workers append a~single response to multiple different dialogues, taking on a random role in each of them.
The conversations are typically rather short \OD{možná rekni počet turnů, ať to nevypadá jako dva} and therefore, full dialogues are collected after few rounds of submissions.
The workers are paid  the same amount of money for every submitted response regardless of whether they play the client or the operator role. \ODdel{and they typically contribute to multiple conversation during one job submission.}\OD{přidal jsem do první věty)}
\ODdel{The contributors are assigned roles randomly.}\OD{ditto}

@@

\section{Dataset Properties} \label{sec:props}
\vspace{-0.50em}
We just started to collect our dataset and so far, we have only collected \OP{62} conversations.
The average length of a conversation is \OP{3.8} turns, meaning that the contributors in both roles reply in average circa three times before the conversation is finished\footnote{The first system utterance is automatically generated and for some conversations, the first client reply is also generated automatically, as described in Section~\ref{sec:async}}.
During an average conversation, \OP{2.4} tasks are requested and \OP{1.9} answered.\OD{Proč ne všechny? To by možná bylo dobrý vysvětlit}
% Typically in \OP{65} \% case the conversation is ended by the client.
% As we mention the conversation are short, taking only from \OP{four to six turns} including first turn with greetings.
% \begin{table}
% \begin{center}
% \begin{tabular}{lrr}
% \hline
% Set   & \# Dialogues & \# Turns \\
% \hline
% % Joint  &  todo &  todo \\
% % /a/SSD/oplatek/e2end/log/2016-06-08-17-31-38.400-dstc-INDEP_labels-d0.7-w100-e100/
% % /a/SSD/oplatek/e2end/log/TEST-ORIGINAL-2016-06-08-17-31-38.400dstc-INDEP_labels-d0.7-w100-e100-reward-0.9080-step-0036224
% Train  &   ? & ? \\
% Dev &   ? & ? \\
% Test &   ? & ? \\
% \hline
% \end{tabular}
% \caption{Accuracy on development and test set}
% \vspace{-2em}
% \end{center}
% \label{tab:props}
% \end{table}
During the data collection process we discarded around \OP{35} \% of replies so far because the utterances were of low quality.
Note that we discard only the low-quality utterance; the prefix of the conversation is submitted for finishing the conversation in a next round of CF tasks.
Once we collect enough conversations, we intend to split them into training, development and test set. % (see Table~\ref{tab:props}).

@@

There is a~significant amount of work which used Wizard-of-Oz experiments~\cite{whittaker2002fish,walker1997evaluating,rieser2008learning} for studying linguistic properties of dialogues, evaluating proof-of-concept\OD{proof of concept čeho??} or even collecting bootstrap training data but to our knowledge, no other work than~\cite{wen2016network} have used cheap crowdsourcing workers to collect a~full training dataset for supervised learning of dialogue management or end-to-end conversations.

\section{Conclusion and Future work} \label{sec:conc}
\vspace{-0.50em}
We present a new human-human dialogue dataset with annotation of user intention in the form of operator's database calls.
We also introduced a novel data collection setting which resembles work of operators in call centers and introduces minimum overhead to crowdsourcing workers.
% TO mi prijde ze v call -centrech delaji stejne\OD{, apart from stating their replies in natural language (?)}
The collected dialogues are published under Creative Commons 4.0 BY-SA license and available for download \ODdel{at {\it anonymized}}.\OD{Napsal bych radši do footnotu “URL will be provided in the camera-ready version of the paper”).}  % lindat\footnote{todo where}.

@@

\vspace{-1.40em}
\subsubsection*{Acknowledgments}
We would like to thank Ondřej Dušek for useful comments.
This research was partly funded by the Ministry of Education, Youth and Sports of the Czech Republic under the grant agreement LK11221, core research funding, grant GAUK 1915/2015, and also partially supported by SVV project number 260 333.\OD{Pro anonymizaci tuhle sekci zatím vynech. V plné verzi bys měl asi poděkovat i Lindatu.} 
% We gratefully acknowledge the support of NVIDIA Corporation with the donation of the Tesla K40c GPU used for this research.
% Cloud computational resources were provided by the MetaCentrum under the program LM2010005 and the CERIT-SC under the program Center CERIT Scientific Cloud, part of the Operational Program Research and Development for Innovations, Reg.\ no. CZ.1.05/3.2.00/08.0144.

>>>>

\title{A Dataset of Operator-client Dialogues Aligned with Database Queries for End-to-end training}

@@

\maketitle
% \OP{Fill missing values about the dataset collected so far} \\
% \OP{grammar check} \\

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}\label{sec:intro}
\vspace{-0.50em}
We present a new dataset of human-human task-oriented conversations in the restaurant information domain, suitable for supervised training of autonomous systems. 
We are currently collecting data for the set using crowdsourcing. We have collected 62 dialogues so far; more than 700 dialogues are planned for the final version of the dataset.\footnote{We expect to release the set before the camera-ready deadline.}

We aim at representing the conversation in a way that makes it easy to train an automated system to replace a human operator. 
Our dataset contains easy-to-collect high-quality transcriptions of the client and operator actions during conversations.
We introduce a~very little overhead by collecting database calls in addition to the transcription of the conversation.
In fact, we mimic very closely a~real situation in call centers where operators search for answers through a database user interface. 
Just logging the calls to the task database provide us with information of a similar quality as a full manual dialogue state annotation.
Tracking the database calls in task oriented systems together with conversation transcription should not introduce significant overhead during the data collection, but should provide a similar amount of supervision for training an end-to-end conversational agent as using fully annotated dialogue state.

Current Spoken Dialogue Systems (SDS) are either handcrafted and use no training data~\cite{duvsek2014alex,raux2005let} but require non-trivial amount of expert work, or they are gradually improved from initial policy through live user interaction~\cite{young2010hidden,gasic2011line}.
Recently, SDS have also been trained using supervised learning in an end-to-end manner~\cite{wen2016network,williams2016end}.\footnote{The~work of \cite{williams2016end} also fine-tuned the conversation with reinforcement learning after the supervised learning stage.}
To train a system using reinforcement learning, one only needs to collect enough live user conversation containing explicit feedback.
However, the feedback signal is harder to interpret than supervised annotation: Thousands of live conversations are required to improve a rather simple policy.\cite{gasic2011line}
Supervised learning methods reduced the number of conversations needed for training a reasonable policy down to a few hundreds\cite{wen2016network}, but require explicit annotation for all components used in the dialogue system.\footnote{To our knowledge, all current systems require full dialogue state annotation as a minimum~\cite{wen2016network,young2010hidden}.}
With the dialogue state being a simplification of the dialogue history with no broadly-accepted form, it is very expensive to collect such annotated data because the dialogue state typically differs among domains and its structure is hard to explain to annotators.
In this paper, we focus on collecting a supervised training set with annotation rich enough so that supervised models similar to~\cite{wen2016network} can be trained with a few hundreds of dialogues, yet much easier to collect than previous methods.

We believe that our dataset dataset can be used for first experiments in training end-to-end systems using supervised learning without explicit dialogue state annotation.
The restaurant information domain used in our dataset is well established thanks to dialogue state tracking (DST) challenges~\cite{williams2013dstc1,henderson2014dstc2,henderson2014dstc3}. 
The DST challenges proved that the domain is of a reasonable complexity.
In addition, the challenges showed that the DST task is solvable by architectures which may be extended to end-to-end conversational agents~\cite{platek2016recurrent,vodolan2015hybrid,henderson2014word}.
Note that our data-collection method is completely domain independent.

The paper is structured as follows: Section~\ref{sec:repre} motivates the annotations and collection procedure used in our dataset.
In Section~\ref{sec:collection}, we introduce our collection process using crowdsourcing.
Section~\ref{sec:props} presents the dataset properties, and we list related work in Section~\ref{sec:related}.
We conclude the paper and suggest future work in~Section~\ref{sec:conc}.

@@

\section{Supervised Feedback for Task-oriented Dialogue} \label{sec:repre}
\vspace{-0.50em}
In this paper, we assume that we need to train a~task-oriented conversational agent in a well-defined domain.
We suppose that the agent has a task database\footnote{In the Cambridge restaurant domain the database is a simple table containing information about restaurants.} at hand and plays the role of the {\it operator}.
The other interlocutor in the conversation is a~human {\it client} that seeks information stored in the database.

The task of building a conversational agents is traditionally simplified by creating pipeline of subtasks: each solved by specialised components: automatic speech recognition (ASR), language understanding (LU) unit, dialogue tracker (DT), dialogue manager (DM), natural language generator (NLG) and text-to-speech (TTS) module~\cite{duvsek2014alex}.
The ASR~\cite{platek2014free} and TTS~\cite{taylor2009text} modules can be easily trained from data without understanding the meaning of the data and there are typically domain independent.
The crucial task of conversation agents is to understand the dialogue history and respond with a reply which has the greatest expected benefit for the agent.
The task of understanding and reply generation is traditionally solved by the text-to-text pipeline of LU, DT, DM, and NLG trained using just in-domain data~\cite{gasic2011line,jurvcivcek2014factored,duvsek2016sequence} annotated at level of each component.
Our datasets provides just the textual input-output transcriptions of in~domain conversations and simple annotations in form of database calls.
We expect that supervised models will be able model the meaning of the history and select its reply only from the transcriptions and the annotation.

% Me to nesedi jako related work - related work je o sbirani dat
% Tohle me prijde zduvodneni, ze takovy (maly, supervised) dataset dava smysl
% Zatim nechavam zde: \OD{následující dva odstavce zní dost jako “related work”... možná bych to tam částečně popřesouval? a tady nechal jen ten statement, že stačí málo trénovacích dat?}
It was shown that a few hundreds of annotated domain specific conversations are needed to train a relatively well performing LU~\cite{jurvcivcek2014factored} as well as Dialogue State Tracking~\cite{young2010hidden} components.
The work of~\cite{duvsek2016sequence} and~\cite{mairesse2010phrase} showed that only several hundreds of turns with appropriate annotation is needed for training a usable NLG unit in simple domains.
Even the crucial task of action selection can be trained using a reinforcement learning dialogue manager and few thousands conversations despite the fact that rewards are only provided at the end of a dialogue~\cite{gasic2011line}.

@@

% We realize that a more fine-grained annotation helps to train the models faster, but simply collecting more data is often more beneficial.\OD{citace? a nevím, jestli tady ta věta je nutná. Možná bych vynechal všechno až do “we believe that annotating...”??}
% As a consequence, we regard the works~\cite{wen2016network,bordes2016learning,williams2016end} as an important step forward to reducing the need for rich annotation in dialogue agent training.
We realize that annotating the dialogue state according to an expert-handcrafted ontology is both an~artificial and a~very labor-intensive data collection task. 
Therefore, our work aims at collecting conversation with lighter and easier to get annotations.
For our dataset, we collect the operator's database calls instead of dialogue state annotation after each turn
A similar recording setup is known from call centers where the operator is provided with a database interface so that they quickly find relevant information and play the role of a domain expert.
To obtain the dataset, we record conversations between a human operator and a human clients via a crowdsourcing platform, i.e., collecting cheap high quality training data.
% OP the previous version and this much better OD version - what is the pattern here?.\OD{Asi bych tohle dal hned po “eaiser to get annotation”. Pak tu větu “a similar recording setup...” a až na konec “we suggest crowdsourcing”, který bych změnil na “To obtain the dataset, we record conversations between human operators and human clients...”}

@@

\section{Dataset Collection Process} \label{sec:collection}
\vspace{-0.50em}
Our data collection process aims at obtaining natural in-domain conversations.
We selected the restaurant domain because it is convenient for collecting shorter, several turns-long conversations.
Also, it was proven that the domain is on one hand difficult enough that even the state-of-the art systems do not reach human-level performance in the role of the operator~\cite{henderson2014dstc2} and on the other hand, numerous systems~\cite{young2010hidden,gasic2011line,wen2016network} demonstrated their ability to provide information to the clients with a reasonable quality.
We define our domain by choosing the database from the 2nd Dialogue State Tracking Challenge (DSTC2)~\cite{henderson2014dstc2}.
We use the CrowdFlower (CF) crowdsourcing platform to collect the conversations.

@@

We use exactly the same database as provided for the DSTC2 challenge~\cite{henderson2014dstc2}.
The database contains information about 107 restaurants in Cambridge, and their properties are stored in several columns.
We include in brackets the number of different values for each column:
% \OD{Když dáš dvousloupcovou tabulku, tak i ušetříš trochu místa}
\vspace{-0.50em}
\begin{itemize}  % tabulku misto tohohle?
    \item name (107),
    \item price range (4),
    \item area (7),
    \item food (25),
    \item address (101),
    \item phone number (97),
    \item postcode (62).
\end{itemize}
\vspace{-0.50em}

@@

We use this database to prepare client goals for CF users (see Section~\ref{sec:client}).
The database is also available through a simple interface to CF users playing the role of the operator (see Section~\ref{sec:operator}).

@@

The CF worker playing the role of the client is asked to request specific information from the operator – a goal.
They may choose not to seek the goal immediately but submit more appropriate response such as greeting instead.
The goals are displayed to the CF worker in the client role gradually turn-by-turn and may contradict each other.
For example, the client may at first want a to find a restaurant serving Chinese food, but later change their mind and seek British food.

Before submitting a reply, the client is instructed to read the dialogue history and mark the goals which were already presented to the operator, as demonstrated in Figure~\ref{fig:client}.
By marking which goals have already been presented to the operator, we oblige the CF workers to pay attention to the dialogue history before submitting their reply.
% TODO - podmnozinovy check neni naimplementovan a asi by opravdu mel byt \OD{do footnotu explicitně vysvětlit, proč to tak je -- proč nemůžou klikat náhodně (že další user vlastně kontroluje toho předchozího tím, že musí zaškrtnout nadmnožinu dříve zaškrtnutých cílů)?}

@@

\vspace{-1.00em}
\subsection{Operator Interface}
\label{sec:operator}
The operator CF worker is asked to politely address the clients needs according to the information stored in the database.
In order to provide the information to clients, the operator uses the simple database interface depicted in~Figure~\ref{fig:operator}:
They filter the restaurants using a full text search over the database.
The~search interface is implemented in Javascript as a simple substring matching over values in the database.
We used such a simple interface because it is easy use for untrained CF workers.
Multiple constrains can be expressed by two substrings separated by a comma.
The content of the database is intentionally hidden if no filter is specified so that a filter has to be used to provide results.
The CF workers are also instructed to explicitly mark the database rows to which they refer in their answer.
Similarly to the client role, the operator does not have to provide all requested information in a single turn.
It is left up to the~worker which information is provided first.

@@

\vspace{-1.00em}
\subsection{Asynchronous collection without real-time responses}
\label{sec:async}
In this section, we describe how we combine the workers' replies to form a conversation.
We design the crowdsourcing jobs so that the CF contributors are able to work independently of each other.
The roles of client and operator take turns as partial conversations are submitted to CF for collecting a single new response.
As a consequence, a~single conversation is collected from multiple contributors over several job submissions.

@@

In a~single CF task submission, we let the workers append a~single response to multiple different dialogues, taking on a random role in each of them.
The conversations are typically rather short circa four turns and therefore, full dialogues are collected after few rounds of submissions.
The workers are paid  the same amount of money for every submitted response regardless of whether they play the client or the operator role.

@@

\section{Dataset Properties} \label{sec:props}
\vspace{-0.50em}
We just started to collect our dataset and so far, we have only collected \OP{62} conversations.
The average length of a conversation is \OP{3.8} turns, meaning that the contributors in both roles reply in average circa three times before the conversation is finished\footnote{The first system utterance is automatically generated and for some conversations, the first client reply is also generated automatically, as described in Section~\ref{sec:async}}.
During an average conversation, \OP{2.4} goals are requested and \OP{1.9} answered.
There are two reason why there is more goals requested than answered.
We saw a rare case when the goal was actually answered, but was not left marked as unanswered.
However, much more common case is that the client asks for several goals e.g. phone and address, but he is satisfied if the operator provides just one of the goals e.g. phone. 
% Typically in \OP{65} \% case the conversation is ended by the client.
% As we mention the conversation are short, taking only from \OP{four to six turns} including first turn with greetings.
% \begin{table}
% \begin{center}
% \begin{tabular}{lrr}
% \hline
% Set   & \# Dialogues & \# Turns \\
% \hline
% % Joint  &  todo &  todo \\
% % /a/SSD/oplatek/e2end/log/2016-06-08-17-31-38.400-dstc-INDEP_labels-d0.7-w100-e100/
% % /a/SSD/oplatek/e2end/log/TEST-ORIGINAL-2016-06-08-17-31-38.400dstc-INDEP_labels-d0.7-w100-e100-reward-0.9080-step-0036224
% Train  &   ? & ? \\
% Dev &   ? & ? \\
% Test &   ? & ? \\
% \hline
% \end{tabular}
% \caption{Accuracy on development and test set}
% \vspace{-2em}
% \end{center}
% \label{tab:props}
% \end{table}
During the data collection process we discarded around \OP{35} \% of replies so far because the utterances were of low quality.
Note that we discard only the low-quality utterance; the prefix of the conversation is submitted for finishing the conversation in a next round of CF tasks.
Once we collect enough conversations, we intend to split them into training, development and test set. % (see Table~\ref{tab:props}).

@@

There is a~significant amount of work which used Wizard-of-Oz experiments~\cite{whittaker2002fish,walker1997evaluating,rieser2008learning} for studying linguistic properties of dialogues, evaluating proof-of-concept of a~dialogue system or even collecting bootstrap training data.
However, to our knowledge, no other work than~\cite{wen2016network} have used cheap crowdsourcing workers to collect a~full training dataset for supervised learning of dialogue management or end-to-end conversations.

\section{Conclusion and Future work} \label{sec:conc}
\vspace{-0.50em}
We present a new human-human dialogue dataset with annotation of user intention in the form of operator's database calls.
We also introduced a novel data collection setting which resembles work of operators in call centers and introduces minimum overhead to crowdsourcing workers.
The collected dialogues are published under Creative Commons 4.0 BY-SA license.\footnote{URL will be provided in the camera-ready version of the paper}  % lindat\footnote{todo where}.

@@

% FIXME hidden for anonymised submission
% \vspace{-1.40em}
% \subsubsection*{Acknowledgments}
% We would like to thank Ondřej Dušek for useful comments.
% This research was partly funded by the Ministry of Education, Youth and Sports of the Czech Republic under the grant agreement LK11221, core research funding, grant GAUK 1915/2015, and also partially supported by SVV project number 260 333.
% It used language resources stored and distributed by the LINDAT/CLARIN project of the Ministry of Education, Youth and Sports of the Czech Repub- lic (project LM2015071).
% We gratefully acknowledge the support of NVIDIA Corporation with the donation of the Tesla K40c GPU used for this research.
% Cloud computational resources were provided by the MetaCentrum under the program LM2010005 and the CERIT-SC under the program Center CERIT Scientific Cloud, part of the Operational Program Research and Development for Innovations, Reg.\ no. CZ.1.05/3.2.00/08.0144.
